Quasi-Newton Methods Comparision using Ackley, Beale, Booth, Matyas, Rastrigin and RosenBrock Functions

### 2022-12-19 paper/new/article.tex
Initial Versioning of Article and Latex Builder

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{mathtools}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{microtype}
\usepackage{float}
\usepackage{adjustbox}
\usepackage{booktabs,makecell,tabularx}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{verbatim}
\usepackage{xcolor}
\usepackage{graphics} % for pdf, bitmapped graphics files
\usepackage{epsfig} % for postscript graphics files
\usepackage{mathptmx} % assumes new font selection scheme installed
\usepackage{multicol}
\usepackage{float}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage{booktabs}
\restylefloat{table}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}
\title{Quasi-Newton Methods Comparision using Ackley, Beale, Booth, Matyas, Rastrigin and RosenBrock Functions}
\author{
	\IEEEauthorblockN{Augusto Mathias Adams\IEEEauthorrefmark{1}, Caio Phillipe Mizerkowski\IEEEauthorrefmark{2}, Christian Piltz Araújo\IEEEauthorrefmark{3} and Vinicius Eduardo dos Reis\IEEEauthorrefmark{4}}\\
	\IEEEauthorblockA{\IEEEauthorrefmark{1}GRR20172143, augusto.adams@ufpr.br, \IEEEauthorrefmark{2}GRR20166403, caiomizerkowski@gmail.com,\\ \IEEEauthorrefmark{3}GRR20172197, christian0294@yahoo.com.br, \IEEEauthorrefmark{4}GRR20175957, eduardo.reis02@gmail.com}
}

@@

The values again are rounded. The matter is the mdian value: it informs us the result that
we are like to obtain when running any algorithm to solve for minimum. As it seems, for all
algorithms is expected to find the minimun of Ackley Function.

@@

The Ackley function has a narrow space around the optimal solution and,
altough specially LMA is of rapid convergence, it iterated 38 times to find
the optimal value, probably because it walked around the solution
before reach it. All algorithms were very slow to converge and the most expensive
are LMA and LBFGS.

Altough the column F. Value points to the the same value, this is a rounded value
and the real values are os order $10^{-22} \approx 10^{-14}$.

@@

The isolines of Ackley Function and convergence lines for all algorithms are shown in Figure~\ref{fig:ackley}:\begin{figure}[H]
\centering
\caption{Isolines and convergence line for Ackley Function}
\label{fig:ackley}
\includegraphics[scale=0.5]{images/ackley.jpg}
\end{figure}
The isolines for Ackley Function shows that there are at least 4 pitfalls near ther optimal solution, so, the search space needs to be reduced to \$[-0.05, 0.05]\$ to avoid wrong convergence. All the algorithms converges quite smoothly following a straight line\subsection{Beale Function}
\label{beale2D}

@@

@@

The optimal solution for Beale Function is $[3, 0.5]$ and the rounded values
of Table~\ref{detailedsolutions:beale} points to the same value. The error of
these values are of order $10^{-13}$ os less.

@@

The isolines of Beale Function and convergence lines for all algorithms are shown i Figure~\ref{fig:beale}:\begin{figure}[H]
\centering
\caption{Isolines and convergence line for Beale Function}
\label{fig:beale}
\includegraphics[scale=0.5]{images/beale.jpg}
\end{figure}
The isolines for Beale Function shows that there are a large plateau near the solution. For an unknown reason the best algorithm had 80\% of performance at its best. Quasi-Newton algorithms suffers to converge when the gradient is less significant.\subsection{Booth Function}
\label{booth2D}

@@

@@

@@

@@

The best solutions of all algorithms for Booth Function, obtained using the minimal
distance of the solution, are shown in Table~\ref{solutions:booth}:
\begin{table}[H]
\centering
\caption{Best Fits For Booth Function}
\label{solutions:booth}
\begin{tabular}{llrrr}
\toprule
 Alg. &    Sol. &  Iter. &  F. Eval &  F. Value \\
\midrule
  dfp & $S_{1}$ &      4 &        6 &      0.00 \\
 bfgs & $S_{2}$ &      2 &        5 &      0.00 \\
lbfgs & $S_{3}$ &      5 &       21 &      0.00 \\
  lma & $S_{4}$ &     10 &       11 &      0.00 \\
\bottomrule
\end{tabular}
\end{table}

Altough the column F. Value points to the the same value, this is a rounded value
and the real values are os order $10^{-22} \approx 10^{-14}$.

@@

\subsubsection{Isolines and Convergence line}
\label{isolinesbooth2D}

\begin{figure}[H]
\centering
\caption{Isolines and convergence line for Booth Function}
\label{fig:booth}
\includegraphics[scale=0.5]{images/booth.jpg}
\end{figure}
\subsection{Matyas Function}
\label{matyas2D}

@@

@@

@@

@@

\subsubsection{Best Fits}
\label{bestfitsmatyas2D}

@@

@@

\subsubsection{Isolines and Convergence line}
\label{isolinesmatyas2D}

\begin{figure}[H]
\centering
\caption{Isolines and convergence line for Matyas Function}
\label{fig:matyas}
\includegraphics[scale=0.5]{images/matyas.jpg}
\end{figure}
\subsection{Rastrigin Function}
\label{rastrigin2d2D}

@@

@@

@@

@@

\subsubsection{Best Fits}
\label{bestfitsrastrigin2d2D}

@@

@@

@@

\begin{figure}[H]
\centering
\caption{Isolines and convergence line for Rastrigin Function}
\label{fig:rastrigin2d}
\includegraphics[scale=0.5]{images/rastrigin2d.jpg}
\end{figure}
\subsection{Rosenbrock Function}
\label{rosenbrock2d2D}

@@

@@

@@

@@

\subsubsection{Best Fits}
\label{bestfitsrosenbrock2d2D}

@@

@@

@@

\begin{figure}[H]
\centering
\caption{Isolines and convergence line for Rosenbrock Function}
\label{fig:rosenbrock2d}
\includegraphics[scale=0.5]{images/rosenbrock2d.jpg}
\end{figure}

\section{4D Function versions}
\label{functions4D}

@@

@@

\subsubsection{Statistical Analysis of The Solutions}
\label{statisticalanalysisrastrigin4d4D}

@@

\subsubsection{Best Fits}
\label{bestfitsrastrigin4d4D}

@@

@@

@@

@@

\subsubsection{Statistical Analysis of The Solutions}
\label{statisticalanalysisrosenbrock4d4D}

@@

@@

@@

@@

@@

@@

\subsubsection{Statistical Analysis of The Solutions}
\label{statisticalanalysisrastrigin30d30D}

@@

\subsubsection{Best Fits}
\label{bestfitsrastrigin30d30D}

@@

@@

@@

@@

\subsubsection{Statistical Analysis of The Solutions}
\label{statisticalanalysisrosenbrock30d30D}

@@

@@

@@

@@

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{mathtools}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{microtype}
\usepackage{float}
\usepackage{adjustbox}
\usepackage{booktabs,makecell,tabularx}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{verbatim}
\usepackage{xcolor}
\usepackage{graphics} % for pdf, bitmapped graphics files
\usepackage{epsfig} % for postscript graphics files
\usepackage{mathptmx} % assumes new font selection scheme installed
\usepackage{multicol}
\usepackage{float}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\restylefloat{table}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}
\title{Quasi-Newton Methods Comparision using Ackley, Beale, Booth, Matyas, Rastrigin and RosenBrock Functions}
\author{
	\IEEEauthorblockN{Augusto Mathias Adams\IEEEauthorrefmark{1}, Caio Phillipe Mizerkowski\IEEEauthorrefmark{2}, Christian Piltz Araújo\IEEEauthorrefmark{3} and Vinicius Eduardo dos Reis\IEEEauthorrefmark{4}}\\
	\IEEEauthorblockA{\IEEEauthorrefmark{1}GRR20172143, augusto.adams@ufpr.br, \IEEEauthorrefmark{2}GRR20166403, caiomizerkowski@gmail.com,\\ \IEEEauthorrefmark{3}GRR20172197, christian0294@yahoo.com.br, \IEEEauthorrefmark{4}GRR20175957, eduardo.reis02@gmail.com}
}

@@

The values again are rounded. The matter is the median value: it informs us the result that
we are like to obtain when running any algorithm to solve for a minimum. As it seems, for all
algorithms is expected to find the minimun of Ackley Function.

@@

The Ackley function has a narrow space around the optimal solution and,
although specially LMA is of rapid convergence, it iterated 38 times to find
the optimal value. All algorithms were very slow to converge and the most expensive
are LMA and LBFGS.

Although the column F. Value points to the the same value, this is a rounded value
and the real values are of order $10^{-22} \approx 10^{-14}$.

@@

The isolines of Ackley Function and convergence lines for all algorithms are shown in Figure~\ref{fig:ackley}:\begin{figure}[H]
\centering
\caption{Isolines and convergence line for Ackley Function}
\label{fig:ackley}
\includegraphics[scale=0.5]{images/ackley.jpg}
\end{figure}
The isolines for Ackley Function shows that there are at least 4 pitfalls near the optimal solution, so, the search space needs to be reduced to $[-0.05, 0.05]$ to avoid wrong convergence. All the algorithms converges quite smoothly following a straight line\subsection{Beale Function}
\label{beale2D}

@@

The Beale Function seems to have a plateau near the solution, as
it is shown in Section~\ref{isolinesbeale2D}.

@@

The optimal solution for Beale Function is $\left[3, 0.5\right]$ and the rounded values
of Table~\ref{detailedsolutions:beale} points to the same value. The error of
these values are of order $10^{-13}$ os less.

@@

The isolines of Beale Function and convergence lines for all algorithms are shown i Figure~\ref{fig:beale}:\begin{figure}[H]
\centering
\caption{Isolines and convergence line for Beale Function}
\label{fig:beale}
\includegraphics[scale=0.5]{images/beale.jpg}
\end{figure}
The isolines for Beale Function shows that there are a large plateau near the solution. For this reason we believe that the best algorithm had 80\% of performance at its best. Quasi-Newton algorithms suffers to converge when the gradient is less significant.\subsection{Booth Function}
\label{booth2D}

@@

The convergence report for the Booth Function is shown in Table~\ref{convergence:booth}:

@@

All algorithms converged 100 times, using 100 different initial solutions,
for a constrained search space of $\left[0, 4\right]$ . This search space is around
the optimal solution to avoid wrong convergence to a local minimum. In this search space,
Booth Function has a well defined valley that has the solution as its center, as it is shown
in Section~\ref{isolinesbooth2D}.

@@

The values again are rounded. The median informs us that, for all
algorithms is expected to find the minimun of Booth Function.

@@

The best solutions of all algorithms for Booth Function, obtained using the minimal
distance of the solution, are shown in Table~\ref{solutions:booth}:

\begin{table}[H]
\centering
\caption{Best Fits For Booth Function}
\label{solutions:booth}
\begin{tabular}{llrrr}
\toprule
 Alg. &    Sol. &  Iter. &  F. Eval &  F. Value \\
\midrule
  dfp & $S_{1}$ &      4 &        6 &      0.00 \\
 bfgs & $S_{2}$ &      2 &        5 &      0.00 \\
lbfgs & $S_{3}$ &      5 &       21 &      0.00 \\
  lma & $S_{4}$ &     10 &       11 &      0.00 \\
\bottomrule
\end{tabular}
\end{table}

Although the column F. Value points to the the same value, this is a rounded value
and the real values are os order $10^{-22} \approx 10^{-14}$.

The best solutions of all algorithms for Beale Function, indicated as
$S_{1}$, $S_{2}$, $S_{3}$ and $S_{4}$ in Table~\ref{solutions:booth}, are shown
in Table~\ref{detailedsolutions:booth}:

@@

The optimal solution for Booth Function is $\left[1, 3\right]$ and the rounded values
of Table~\ref{detailedsolutions:booth} points to the same value. The error of
these values are of order $10^{-13}$ os less.
\subsubsection{Isolines and Convergence line}
\label{isolinesbooth2D}

The isolines of Booth Function and convergence lines for all algorithms are shown i Figure~\ref{fig:booth}:\begin{figure}[H]
\centering
\caption{Isolines and convergence line for Booth Function}
\label{fig:booth}
\includegraphics[scale=0.5]{images/booth.jpg}
\end{figure}
The Figure~\ref{fig:booth} shows that Booth Function has a well defined valley near $[1, 3]$. \subsection{Matyas Function}
\label{matyas2D}

@@

The convergence report for the Matyas Function is shown in Table~\ref{convergence:matyas}:

@@

All algorithms converged 100 times, using 100 different initial solutions,
for a search space of $\left[-10, 10\right]$ . In this search space,
Matyas Function has a well defined valley that has the solution as its
center, as it is shown in Section~\ref{isolinesmatyas2D}.

@@

The minimal. maximal, mean and median values of the solutions are shown in Table~\ref{function_values:matyas}:

@@

The values again are rounded. The median informs us that, for all
algorithms is expected to find the minimun of Matyas Function.
\subsubsection{Best Fits}
\label{bestfitsmatyas2D}

The best solutions of all algorithms for Booth Function, obtained using the minimal
distance of the solution, are shown in Table~\ref{solutions:matyas}:

@@

The algorithms DFP, BFGS and LBFGS have comparable performances, while LMA
is the most expensive of all.

Although the column F. Value points to the the same value, this is a rounded value
and the real values are os order $10^{-22} \approx 10^{-14}$.

The best solutions of all algorithms for Matyas Function, indicated as
$S_{1}$, $S_{2}$, $S_{3}$ and $S_{4}$ in Table~\ref{solutions:matyas}, are shown
in Table~\ref{detailedsolutions:matyas}:

@@

The optimal solution for Matyas Function is $\left[0, 0\right]$ and the rounded values
of Table~\ref{detailedsolutions:matyas} points to the same value. The error of
these values are of order $10^{-13}$ os less.
\subsubsection{Isolines and Convergence line}
\label{isolinesmatyas2D}

The isolines of Matyas Function and convergence lines for all algorithms are shown i Figure~\ref{fig:matyas}:\begin{figure}[H]
\centering
\caption{Isolines and convergence line for Matyas Function}
\label{fig:matyas}
\includegraphics[scale=0.5]{images/matyas.jpg}
\end{figure}
The Figure~\ref{fig:matyas} shows that Matyas Function has a well defined valley near $[0, 0]$. \subsection{Rastrigin Function}
\label{rastrigin2d2D}

@@

The convergence report for the Rastrigin Function in 2 dimensions is shown in Table~\ref{convergence:rastrigin2d}:

@@

It is quite sure that all algorithms has good convergence for any algorithm for a
constrained search space of $\left[-0.15, 0.15\right]$. This search space is around
the optimal solution to avoid wrong convergence to a local minimum. In this search space,
Rastrigin Function has a well defined valley that has the solution as its center, as is shown in
Section~\ref{isolinesrastrigin2D}.

@@

The minimal. maximal, mean and median values of the solutions are shown in Table~\ref{function_values:rastrigin2d}:

@@

The values again are rounded. The median informs us that, for all
algorithms is expected to find the minimun of Rastrigin Function.
Although the mean of LBFGS algorithm is greater than zero, it is expected
to converge mora than diverge in the function constrained search space.
\subsubsection{Best Fits}
\label{bestfitsrastrigin2d2D}

The best solutions of all algorithms for Rastrigin Function, obtained using the minimal
distance of the solution, are shown in Table~\ref{solutions:rastrigin2d}:

@@

LMA is the less expensive algorithm to solve Rastrigin in 2 dimensions, while LBFGS
is the most expensive of all. Although it has one more iteration than LMA, it evaluates
the objective function much more times than BFGS, the second most expensive algorithm.

Although the column F. Value points to the the same value, this is a rounded value
and the real values are os order $10^{-22} \approx 10^{-14}$.

The best solutions of all algorithms for Rastrigin Function, indicated as
$S_{1}$, $S_{2}$, $S_{3}$ and $S_{4}$ in Table~\ref{solutions:rastrigin2d}, are shown
in Table~\ref{detailedsolutions:rastrigin2d}:

@@

The Table~\ref{detailedsolutions:rastrigin2d} shows the same solution to all algorithms, because the values are so small
and were rounded to fit on the Table. The differences of the optimal point are of order $10^{-14}$ to $10^{-22}$,
for the LMA, DFP, LBFGS and BFGS algorithms, respectively.

@@

The isolines of Rastrigin Function for 2 dimensions and convergence lines for all algorithms are shown in Figure~\ref{fig:rastrigin2d}:\begin{figure}[H]
\centering
\caption{Isolines and convergence line for Rastrigin Function}
\label{fig:rastrigin2d}
\includegraphics[scale=0.5]{images/rastrigin2d.jpg}
\end{figure}
The isolines for Rastrigin Function shows that there are at least 2 pitfalls near the optimal solution, so, the search space needs to be reduced to $[-0.15, 0.15]$ to avoid wrong convergence. All the algorithms, except BFGS, converges quite smoothly following a straight line\subsection{Rosenbrock Function}
\label{rosenbrock2d2D}

@@

The convergence report for the Rosenbrock Function in 30 dimensions is shown in Table~\ref{convergence:rosenbrock2d}:

@@

Except for DFP, Rosenbrock has good convergence for any algorithm for a constrained search space
of $\left[-1.5, 1.5\right]$. Although the Rosenbrock Function has only the global minimum in a
search space of $\left[-10, 10\right]$, it has a large banana shaped plateau near the optimal
solution, as it is shown in Section~\ref{isolinesrosenbrock2D}. The search space constraint serves
only to limit the number of iterations of each algorithm. The large search space tends to make the algorithm
walks too much to find the solution and tends to exceed the maximum iterations defined in the evaluation
criteria shown in Section~\ref{sec:introduction}.

@@

The minimal. maximal, mean and median values of the solutions are shown in Table~\ref{function_values:rosenbrock2d}:

@@

The values again are rounded. The median informs us that, for all
algorithms is expected to find the minimun of Rosenbrock Function.
Although the mean of DFP algorithm is greater than zero, it is expected
to converge more than diverge in the function constrained search space.
\subsubsection{Best Fits}
\label{bestfitsrosenbrock2d2D}

The best solutions of all algorithms for Rosenbrock Function, obtained using the minimal
distance of the solution, are shown in Table~\ref{solutions:rosenbrock2d}:

@@

LMA is the less expensive algorithm to solve Rosenbrock Function in 2 dimensions, while LBFGS
is the most expensive of all. Although it has comparable iterations with DFP nd BFGS, it evaluates
the objective function twice as much of BFGS, the second most expensive algorithm.

Although the column F. Value points to the the same value, this is a rounded value
and the real values are os order $10^{-22} \approx 10^{-14}$.

The best solutions of all algorithms for Rosenbrock Function, indicated as
$S_{1}$, $S_{2}$, $S_{3}$ and $S_{4}$ in Table~\ref{solutions:rosenbrock2d}, are shown
in Table~\ref{detailedsolutions:rosenbrock2d}:

@@

The optimal point of Rosenbrock function in 2 dimensions is correctly pointed to $\left[1, 1\right]$. The Table~\ref{detailedsolutions:rosenbrock2d}
shows the same solution to all algorithms, because the values are so small and were rounded to fit on the Table. The differences of
the optimal point are of order $10^{-14}$ to $10^{-22}$, for the LMA, DFP, LBFGS and BFGS algorithms, respectively.

@@

The isolines of Rosenbrock Function for 2 dimensions and convergence lines for all algorithms are shown in Figure~\ref{fig:rosenbrock2d}:\begin{figure}[H]
\centering
\caption{Isolines and convergence line for Rosenbrock Function}
\label{fig:rosenbrock2d}
\includegraphics[scale=0.5]{images/rosenbrock2d.jpg}
\end{figure}
The isolines for Rosenbrock Function shows an interesting behaviour  near the optimal solution: the banana shape seems to force all algorithms to choose $x_{2}$ axis to solve first, and then solve for $x_{1}$ axis. The $x_{2}$ axis has probably the most significant derivative for an arbitrary point, so, when the algorithm walks around for solution, it first find the valley and then walks around the valley to find its minumum
\section{4D Function versions}
\label{functions4D}

@@

The convergence report for the Rastrigin Function in 4 dimensions is shown in Table~\ref{convergence:rastrigin4d}:

@@

It is quite sure that all algorithms has good convergence for any algorithm for a
constrained search space of $\left[-0.15, 0.15\right]$. This search space is around
the optimal solution to avoid wrong convergence to a local minimum. In this search space,
Rastrigin Function has a well defined valley that has the solution as its center.
\subsubsection{Statistical Analysis of The Solutions}
\label{statisticalanalysisrastrigin4d4D}

The minimal. maximal, mean and median values of the solutions are shown in Table~\ref{function_values:rastrigin4d}:

@@

The values again are rounded. The median informs us that, for all
algorithms is expected to find the minimun of Rastrigin Function.
\subsubsection{Best Fits}
\label{bestfitsrastrigin4d4D}

The best solutions of all algorithms for Rastrigin Function, obtained using the minimal
distance of the solution, are shown in Table~\ref{solutions:rastrigin4d}:

@@

LMA is the less expensive algorithm to solve Rastrigin in 4 dimensions, while LBFGS
is the most expensive of all. Although it has one more iteration than LMA, it evaluates
the objective function twice than BFGS, the second most expensive algorithm.

Although the column F. Value points to the the same value, this is a rounded value
and the real values are os order $10^{-22} \approx 10^{-14}$.

The best solutions of all algorithms for Rastrigin Function, indicated as
$S_{1}$, $S_{2}$, $S_{3}$ and $S_{4}$ in Table~\ref{solutions:rastrigin4d}, are shown
in Table~\ref{detailedsolutions:rastrigin4d}:

@@

The Table~\ref{detailedsolutions:rastrigin4d} shows the same solution to all algorithms, because the values are so small
and were rounded to fit on the Table. The differences of the optimal point are of order $10^{-14}$ to $10^{-22}$,
for the LMA, DFP, LBFGS and BFGS algorithms, respectively.

@@

The convergence report for the Rosenbrock Function in 30 dimensions is shown in Table~\ref{convergence:rosenbrock4d}:

@@

DFP has poor convergence properties for the Rosenbrock Function with more than 2 dimensions.
The rest have quite the same profile regarding convergence. It is important to note that
although all algorithms does not converge for the presented initial solutions, it does not
diverge at all. Because of the stop criterion of all algorithms, which is the function gradient value,
and the banana shaped valley (plateau) that Rosenbrock function has, we have this behaviour.
\subsubsection{Statistical Analysis of The Solutions}
\label{statisticalanalysisrosenbrock4d4D}

The minimal. maximal, mean and median values of the solutions are shown in Table~\ref{function_values:rosenbrock4d}:

@@

The median value informs us that all algorithms are like to find the solution
for Rosenbrock Function in 4 dimesions. The cases of poor convergence that all algorithms
have are reflected in the mean value. Looking at the Maximum value, it is noted that the mean value is
quite the same percentage shown in Table~\ref{convergence:rosenbrock4d}.

@@

The best solutions of all algorithms for Rosenbrock Function, obtained using the minimal
distance of the solution, are shown in Table~\ref{solutions:rosenbrock4d}:

@@

LMA is the less expensive algorithm to solve Rosenbrock Function in 4 dimensions, while LBFGS
is the most expensive of all. Although it has comparable iterations with DFP nd BFGS, it evaluates
the objective function twice as much of BFGS, the second most expensive algorithm.

Although the column F. Value points to the the same value, this is a rounded value
and the real values are os order $10^{-22} \approx 10^{-14}$.

The best solutions of all algorithms for Rosenbrock Function, indicated as
$S_{1}$, $S_{2}$, $S_{3}$ and $S_{4}$ in Table~\ref{solutions:rosenbrock4d}, are shown
in Table~\ref{detailedsolutions:rosenbrock4d}:

@@

The optimal point of Rosenbrock function in 4 dimensions is correctly pointed to $\left[1, 1, 1, 1\right]$. The Table~\ref{detailedsolutions:rosenbrock4d}
shows the same solution to all algorithms, because the values are so small and were rounded to fit on the Table. The differences of
the optimal point are of order $10^{-14}$ to $10^{-22}$, for the LMA, DFP, LBFGS and BFGS algorithms, respectively.

@@

The convergence report for the Rastrigin Function in 2 dimensions is shown in Table~\ref{convergence:rastrigin30d}:

@@

It is quite sure that all algorithms has good convergence for a
constrained search space of $\left[-0.15, 0.15\right]$. This search space is around
the optimal solution to avoid wrong convergence to a local minimum. In this search space,
Rastrigin Function has a well defined valley that has the solution as its center.
\subsubsection{Statistical Analysis of The Solutions}
\label{statisticalanalysisrastrigin30d30D}

The minimal. maximal, mean and median values of the solutions are shown in Table~\ref{function_values:rastrigin30d}:

@@

The values again are rounded. The median informs us that, for all
algorithms is expected to find the minimun of Rastrigin Function.
\subsubsection{Best Fits}
\label{bestfitsrastrigin30d30D}

The best solutions of all algorithms for Rastrigin Function, obtained using the minimal
distance of the solution, are shown in Table~\ref{solutions:rastrigin30d}:

@@

LMA is the less expensive algorithm to solve Rastrigin in 30 dimensions, while LBFGS
is the most expensive of all. Although it has one more iteration than LMA, it evaluates
the objective function twice than BFGS, the second most expensive algorithm.

Although the column F. Value points to the the same value, this is a rounded value
and the real values are os order $10^{-22} \approx 10^{-14}$.

The best solutions of all algorithms for Rastrigin Function, indicated as
$S_{1}$, $S_{2}$, $S_{3}$ and $S_{4}$ in Table~\ref{solutions:rastrigin30d}, are shown
in Table~\ref{detailedsolutions:rastrigin30d}:

@@

The Table~\ref{detailedsolutions:rastrigin30d} shows the same solution to all algorithms, because the values are so small
and were rounded to fit on the Table. The differences of the optimal point are of order $10^{-14}$ to $10^{-22}$,
for the LMA, DFP, LBFGS and BFGS algorithms, respectively.

@@

The convergence report for the Rosenbrock Function in 30 dimensions is shown in Table~\ref{convergence:rosenbrock30d}:

@@

DFP has poor convergence properties for the Rosenbrock Function with more than 2 dimensions.
The rest have quite the same profile regarding convergence. It is important to note that
although all algorithms does not converge for the presented initial solutions, it does not
diverge at all. Because of the stop criterion of all algorithms, which is the function gradient value,
and the banana shaped valley (plateau) that Rosenbrock function has, we have this behaviour.
\subsubsection{Statistical Analysis of The Solutions}
\label{statisticalanalysisrosenbrock30d30D}

The minimal. maximal, mean and median values of the solutions are shown in Table~\ref{function_values:rosenbrock30d}:

@@

The median value informs us that all algorithms are like to find the solution
for Rosenbrock Function in 4 dimesions. The cases of poor convergence that all algorithms
have are reflected in the mean value. Looking at the Maximum value, it is noted that the mean value is
quite the same percentage shown in Table~\ref{convergence:rosenbrock30d}.

@@

T
he best solutions of all algorithms for Rosenbrock Function, obtained using the minimal
distance of the solution, are shown in Table~\ref{solutions:rosenbrock4d}:

@@

LMA is the less expensive algorithm to solve Rosenbrock Function in 30 dimensions, while DFP
is the most expensive of all.

Although the column F. Value points to the the same value, this is a rounded value
and the real values are os order $10^{-22} \approx 10^{-14}$.

The best solutions of all algorithms for Rosenbrock Function, indicated as
$S_{1}$, $S_{2}$, $S_{3}$ and $S_{4}$ in Table~\ref{solutions:rosenbrock30d}, are shown
in Table~\ref{detailedsolutions:rosenbrock30d}:

@@

The optimal point of Rosenbrock function in 30 dimensions is correctly pointed to $\left[1, 1, \cdots , 1, 1\right]$. The Table~\ref{detailedsolutions:rosenbrock30d}
shows the same solution to all algorithms, because the values are so small and were rounded to fit on the Table. The differences of
the optimal point are of order $10^{-14}$ to $10^{-22}$, for the LMA, DFP, LBFGS and BFGS algorithms, respectively.
